\chapter{System Maintenance}

\section{Environment}

\subsection{Software}
In creating this system have have lots of different software to preform different tasks: Python 3; is a loosely typed 3rd generation programing language. IDLE; is where you physically write your code for python, IDLE is used to write python script as well as run a python script, including displaying errors. SQLite 3; is part of the standard library of python and is used to create and use databases within python. datetime; datetime is part of the standard library of python and is used so programmers can use the time and date in there programs. SQLite inspector; this is a program that displays data with in a database it can also execute queries

\subsection{Usage Explanation}

\subsubsection{python 3}
The reasons I choose to write my system in python firstly is because python is the programing language i am most familiar with however there are a one or two other programs i could have written in. python is also a loosely typed language making it easier to use and understand. python is also easy to installed on any machine making it a good choice when I have write parts of this system from three different machines all with different hardware and software installed on them. python also has a standard library which can be imported into any python script for the programmer to use.

\subsubsection{IDLE}
IDLE is the program in which one write their python code, IDLE is able to save written code as well as run it and display errors. IDLE has an easy to understand bug report format with a feature to jump you to the line of code which is incorrect as well as giving useful information about the type of error and what Modules the incorrect line is part of. this makes IDLE the ideal environment in which to program my system. 

\subsubsection{SQLite 3}
I used SQLite 3 in order to create and access databases from a python script. SQLite 3 has simple syntax making it easy to understand and use, this also makes it possible to create much more complicated queries to access, order and sort data.

\subsubsection{datetime}
i used the datetime library to time stamp certain data being entered into the database such as DeliveryTimeDate and the time of each transaction.

\subsubsection{SQLite inspector}
SQLite inspector is an open source amateur build program which i have chosen to use due to its simplicity, when a database is loaded it displays all the objects in one tab so it it easy to see what object has which attributes and keys. the second tab displays the information table by table with a drop down box to change the table being viewed, this is where i can see the data that is in side the database. finally the third tab has a shell which can execute SQL directly to the currently loaded database, this was useful for quickly entering data for testing

\subsection{Features Used}

\subsubsection{python}
In python I used the import feature in order to import functions from other python files into the main file, i also used the return feature in order to pass parameters between the function.

\subsubsection{IDLE}
IDLE has many useful features writing code the first of which being it has syntax colouring for strings(green), user created functions/classes(orange) and build in functions(purple). IDLE also has an indent feature to help the coder understand what is happening to certain parts of code such as all the code in a function will be indented and the same with while and for loops. to an extent IDLE also has an auto-completion where a text bow will appear and you can select the code you want. IDLE also prompts users about how structure the syntax. finally IDLE has an integrated debugger showing each level of the program it went through before it encountered the error.


\subsubsection{SQLite 3}


\subsubsection{datetime}
The only feature i used of the datetime modal was the datetime.datetime.now() function which gave the date and time of the when it was executed. I used this as it was simple to use and only took up one line of code, I used it to time stamp certain operations in my system such as transactions and delivery times.

\subsubsection{SQLite inspector}
The features of SQLite inspector are strait forward, firstly it has a tab that displays all the objects with their attributes and correct keys in the standard syntax. Secondly it has a tab that views the real data in the system so a user can check their system is working


\section{System Overview}

%use as many subsections as necessary for the system components
\subsection{System Component}

\section{Code Structure}

%use as many subsections as necessary for the code sections
\subsection{Particular Code Section}
%the code below can be uncommented and used to get a code section from a particular file

\section{Variable Listing}

\section{System Evidence}

\subsection{User Interface}

\subsection{ER Diagram}

\subsection{Database Table Views}

\subsection{Database SQL}

\subsection{SQL Queries}

\section{Testing}

\subsection{Summary of Results}

\subsection{Known Issues}

\section{Code Explanations}

\subsection{Difficult Sections}

\subsection{Self-created Algorithms}

\section{Settings}

\section{Acknowledgements}

\section{Code Listing}
\begin{landscape}
\subsection{creating brand table}
\pythonfile[]{./Implementation/command_line/creating_brand_table.py}

\subsection{creating delivery table}
\pythonfile[]{./Implementation/command_line/creating_delivery_table.py}

\subsection{creating delivery-stock table}
\pythonfile[]{./Implementation/command_line/creating_DeliveryStock_table.py}

\subsection{creating location table}
\pythonfile[]{./Implementation/command_line/creating_location_table.py}

\subsection{creating product table}
\pythonfile[]{./Implementation/command_line/creating_product_table.py}

\subsection{creating product-type table}
\pythonfile[]{./Implementation/command_line/creating_ProductType_table.py}

\subsection{creating stock table}
\pythonfile[]{./Implementation/command_line/creating_stock_table.py}

\subsection{creating stock-check table}
\pythonfile[]{./Implementation/command_line/creating_StockCheck_table.py}

\subsection{creating supplier table}
\pythonfile[]{./Implementation/command_line/creating_supplier_table.py}

\subsection{creating transaction table}
\pythonfile[]{./Implementation/command_line/creating_transaction_table.py}

\subsection{creating transactions-product table}
\pythonfile[]{./Implementation/command_line/creating_TransactionsProduct_table.py}

\subsection{creating user table}
\pythonfile[]{./Implementation/command_line/creating_user_table.py}

\subsection{edit brand table}
\pythonfile[]{./Implementation/command_line/edit_brand_table.py}

\subsection{edit delivery table}
\pythonfile[]{./Implementation/command_line/edit_delivery_table.py}

\subsection{edit delivery-stock table}
\pythonfile[]{./Implementation/command_line/edit_DeliveryStock_table.py}

\subsection{edit location table}
\pythonfile[]{./Implementation/command_line/edit_location_table.py}

\subsection{edit product table}
\pythonfile[]{./Implementation/command_line/edit_product_table.py}

\subsection{edit product-type table}
\pythonfile[]{./Implementation/command_line/edit_ProductType_table.py}

\subsection{edit stock table}
\pythonfile[]{./Implementation/command_line/edit_stock_table.py}

\subsection{edit stock-check table}
\pythonfile[]{./Implementation/command_line/edit_StockCheck_table.py}

\subsection{edit supplier table}
\pythonfile[]{./Implementation/command_line/edit_supplier_table.py}

\subsection{edit transaction table}
\pythonfile[]{./Implementation/command_line/edit_Transactions_table.py}

\subsection{edit transactions-product table}
\pythonfile[]{./Implementation/command_line/edit_TransactionsProduct_table.py}

\subsection{edit user table}
\pythonfile[]{./Implementation/command_line/edit_user_table.py}

\subsection{insert brand table}
\pythonfile[]{./Implementation/command_line/insert_new_brand.py}

\subsection{insert delivery table}
\pythonfile[]{./Implementation/command_line/insert_new_delivery.py}

\subsection{insert delivery-stock table}
\pythonfile[]{./Implementation/command_line/insert_new_DeliveryStock.py}

\subsection{insert location table}
\pythonfile[]{./Implementation/command_line/insert_new_location.py}

\subsection{insert product table}
\pythonfile[]{./Implementation/command_line/insert_new_product.py}

\subsection{insert product-type table}
\pythonfile[]{./Implementation/command_line/insert_new_ProductType.py}

\subsection{insert stock table}
\pythonfile[]{./Implementation/command_line/insert_new_stock.py}

\subsection{insert stock-check table}
\pythonfile[]{./Implementation/command_line/insert_new_StockCheck.py}

\subsection{insert supplier table}
\pythonfile[]{./Implementation/command_line/insert_new_supplier.py}

\subsection{insert transaction table}
\pythonfile[]{./Implementation/command_line/insert_new_Transactions.py}

\subsection{insert transactions-product table}
\pythonfile[]{./Implementation/command_line/insert_new_TransactionsProduct.py}

\subsection{insert user table}
\pythonfile[]{./Implementation/command_line/insert_new_user.py}

\subsection{delete}
\pythonfile[]{./Implementation/command_line/delete.py}

\subsection{python command line}
\pythonfile[]{./Implementation/command_line/python_comand_line.py}

\subsection{transaction}
\pythonfile[]{./Implementation/command_line/transaction.py}
\end{landscape}
